---
title: "Data Mining Project"
author: "Khalid"
output: pdf_document
header-includes:
  - \usepackage{lscape}
  - \geometry{landscape}
geometry: margin=1in, landscape
---

# Data Mining Project

### 1. Open file in R

```{r}
data <- read.csv("/visa_number_in_japan.csv")
```

### 2. Look into the content of the data

```{r}
str(data)
```

### 3. Data Cleaning

#### 3.1 Separate the data into their respective year and country

```{r}
years <- unique(data$Year)
countries <- unique(data$Country)

for (year in years) {
  assign(paste0("data_", year), subset(data, Year == year))
}

for (country in countries) {
  country_name <- gsub("[^a-zA-Z0-9]", "_", country)
  assign(paste0("data_", country_name), subset(data, Country == country))
}

ls(pattern = "data_")
```

##### The data is divided into their respective object

##### To check the object

```{r}
str(data_2006)
head(data_2006)
```

```{r}
str(data_Afghanistan)
head(data_Afghanistan)
```

### 4. Data Analysis

#### 4.1 The total number of issued for each of the country through out the years

##### Example: Malaysia

```{r}
library(ggplot2)

Malaysia_data <- subset(data, Country == "Malaysia")

Malaysia_data$Year <- as.numeric(Malaysia_data$Year)
Malaysia_data$Number.of.issued <- as.numeric(Malaysia_data$Number.of.issued)

ggplot(Malaysia_data, aes(x = Year, y = Number.of.issued)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "red", size = 2) +
  labs(title = "Number of Visas Issued for Malaysia (2006-2017)",
       x = "Year",
       y = "Number of Visas Issued") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2006, 2017, 1)) +
  scale_y_continuous(labels = scales::comma)
```

#### 4.2 The total number of issued for each of the country in a specific year

##### Example: 2006

```{r}
library(ggplot2)

data_2006 <- subset(data, Year == 2006)

data_2006$Number.of.issued <- as.numeric(data_2006$Number.of.issued)

top_10_countries <- data_2006[order(-data_2006$Number.of.issued), ][1:10, ]

ggplot(top_10_countries, aes(x = reorder(Country, -Number.of.issued), y = Number.of.issued, fill = Country)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = rainbow(10)) +
  labs(title = "Top 10 Countries by Number of Visas Issued in 2006",
       x = "Country",
       y = "Number of Visas Issued") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = scales::comma)
```

##### Example: 2017

```{r}
library(ggplot2)

data_2017 <- subset(data, Year == 2017)

data_2017$Number.of.issued <- as.numeric(data_2017$Number.of.issued)

top_10_countries <- data_2017[order(-data_2017$Number.of.issued), ][1:10, ]

ggplot(top_10_countries, aes(x = reorder(Country, -Number.of.issued), y = Number.of.issued, fill = Country)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = rainbow(10)) +
  labs(title = "Top 10 Countries by Number of Visas Issued in 2017",
       x = "Country",
       y = "Number of Visas Issued") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = scales::comma)
```

#### 4.3 The total number of issued for each year through out the dataset

```{r}
library(dplyr)

data_summary <- data %>% group_by(Year) %>% summarise(total_issues = sum(Number.of.issued, na.rm = TRUE))

ggplot(data_summary, aes(x = factor(Year), y = total_issues)) +
  geom_line(group = 1, color = "red", size = 1) +
  geom_point(color = "blue", size = 3) +
  labs(title = "Total Issues by Year", x = "Year", y = "Total Issues") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### 5. Time Series Analysis

#### 5.1 Preprocessing

```{r}
library(dplyr)

data_summary <- data %>% group_by(Year) %>% summarise(total_issues = sum(Number.of.issued, na.rm = TRUE))

print(data_summary)
```

#### 5.2 Time Series Plot

```{r}
library(ggplot2)

ggplot(data_summary, aes(x = Year, y = total_issues)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "red", size = 2) +
  labs(title = "Total Issues Over Time", x = "Year", y = "Total Issues") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

#### 5.3 Time Series Decomposition

```{r}
total_issues_ts <- ts(data_summary$total_issues, start = min(data_summary$Year), frequency = 1)

print(total_issues_ts)
```

#### 5.4 Modeling with ARIMA

```{r}

library(forecast)

arima_model <- auto.arima(total_issues_ts)

forecasted_values <- forecast(arima_model, h = 5)

plot(forecasted_values)
```
